Project 1 Checkpoint

### 2015-02-27 project1/checkpoint/main.tex
Adding RNG discussion

>>>>

Alongside the NGSIM data set \cite{ngsim}, we are also dependent on the browser for much of our runtime configuration.
In particular, we rely on the random number generation capabilities of the browser for our entire source of randomness.
JavaScript provides a built-in implementation \cite{ecmascriptmath} \texttt{Math.random()}, which provides a uniformly
distributed random number between 0 and 1. The standard also specifies that the implementation is vendor-dependent.
This means that the "randomness" of \texttt{Math.random()} is dependent on the browser. Because of this, I've provided
a web page to calculate a simple $\chi^2$ statistic for a sample \cite{rngtester}. I've tested on Safari, Firefox, and
Chrome with generally solid results, despite the fact that their implementations are different
\cite{rngimplementation}. However, Hyland \cite{rngimplementation} does warn the reader about the caveats associated
with the native browser implementation of random numbers. However, these issues are not terribly important for a
simulation of this simplicity.
